Equalizer Programming Guide

### 2008-10-21 Developer/ProgrammingGuide/paper.tex
Programming Guide: Minor tweak.
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.3.13 for Equalizer 0.5.5+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Version for Equalizer 0.5\\
    1.3.1   & May 02, 2008 & Add \sref{sStatistics}, improved images based on 1.2 print\\
    1.3.2   & May 05, 2008 & Add network distribution on eqPly model data\\
    1.3.3   & May 10-19, 2008 & add \aref{aFileFormat}\\
    1.3.4   & July 3, 2008 & Update \sref{sStatistics}\\
    1.3.5   & July 7, 2008 & Update after namespace naming cleanup\\
    1.3.6   & July 20, 2008 & Add accum and samples to \aref{aFileFormat}, add \sref{sDrawableConfig}\\
    1.3.7   & Aug 22, 2008 & Update \sref{sEqplyWIndow} with OSWindow changes\\
    1.3.8   & Aug 25, 2008 & Update \sref{sEventHandling} with OSWindow changes\\
    1.3.9   & Aug 29, 2008 & Update \sref{sEventHandling}: event handling cleanup\\
    1.3.10  & Oct 7, 2008  & Updated to reflect 2D pixel compounds\\
    1.3.11  & Oct 13, 2008 & Updated to reflect eq::net::Object cleanup\\
    1.3.12  & Oct 16, 2008 & Added \sref{sView}\\
    1.3.13  & Oct 17, 2008 & Minor update in \sref{sMessagePump}\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

The hostname is the IP address or (resolvable) host name. When used for
the server, the server binds its listening socket only to the specified
name.

A server or node may have multiple connection descriptions. A server
binds to all provided connection descriptions. For a node, all
connection descriptions are used while trying to establish a connection
to the node. When auto-launched by the server, all connection
descriptions are passed to the launched node process, which binds to all
provided descriptions.

>>>>

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.3.14 for Equalizer 0.5.5+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Version for Equalizer 0.5\\
    1.3.1   & May 02, 2008 & Add \sref{sStatistics}, improved images based on 1.2 print\\
    1.3.2   & May 05, 2008 & Add network distribution on eqPly model data\\
    1.3.3   & May 10-19, 2008 & add \aref{aFileFormat}\\
    1.3.4   & July 3, 2008 & Update \sref{sStatistics}\\
    1.3.5   & July 7, 2008 & Update after namespace naming cleanup\\
    1.3.6   & July 20, 2008 & Add accum and samples to \aref{aFileFormat}, add \sref{sDrawableConfig}\\
    1.3.7   & Aug 22, 2008 & Update \sref{sEqplyWIndow} with OSWindow changes\\
    1.3.8   & Aug 25, 2008 & Update \sref{sEventHandling} with OSWindow changes\\
    1.3.9   & Aug 29, 2008 & Update \sref{sEventHandling}: event handling cleanup\\
    1.3.10  & Oct 7, 2008  & Updated to reflect 2D pixel compounds\\
    1.3.11  & Oct 13, 2008 & Updated to reflect eq::net::Object cleanup\\
    1.3.12  & Oct 16, 2008 & Added \sref{sView}\\
    1.3.13  & Oct 17, 2008 & Minor update in \sref{sMessagePump}\\
    1.3.14  & Oct 21, 2008 & Improved \sref{sConnectionDescription}\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

The hostname is the IP address or (resolvable) host name. A server or
node may have multiple connection descriptions.

A server listens on all provided connection descriptions. If no hostname
is specified for a server connection description, it listens to
INADDR\_ANY, and is therefore reachable on all interfaces. If the
server's hostname is specified, the listening socket is bound to this
address. If any hostname given is not resolvable, or any port can not be
used, server initialization will fail.

For a node, all connection descriptions are used while trying to
establish a connection to the node. When auto-launched by the server,
all connection descriptions of the node are passed to the launched node
process, which binds to all provided descriptions.
